\documentclass[a4paper,11pt]{article}
\usepackage[strict]{changepage}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage[a4paper]{geometry}
\usepackage[T1]{fontenc}
\usepackage{bookmark, latexsym, titlesec, verbatim, enumitem, marvosym, fancyhdr, tabularx, fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \geometry{left=1.9cm, top=1.8cm, right=1.9cm, bottom=1.8cm, footskip=.5cm}
\geometry{left=14.11 mm, top=18mm, right=14.11mm, bottom=15mm, footskip=.5cm}

\urlstyle{same}

\raggedbottom \raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%------------------ Custom commands ------------------- 
\def\Plus{\texttt{+}}
\def\Minus{\texttt{-}}

\newcommand{\techSkill}[2]{\item\small \textbf{#1:} #2 \vspace{-5pt}}
\newcommand{\techSkillListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\techSkillListEnd}{\end{itemize}}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingAlt}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #5} \\
      \textit{\small#4}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.977\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[4]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
      \textit{\small#3} & \textit{\small #4}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeadingAlt}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=-0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\cvrank}[2]{\small{\textit{#1} \textbf{#2} $\bullet$}}
\newcommand{\cvrankend}[2]{\small{\textit{#1} \textbf{#2} \\ }
}


\newcommand{\extracurr}[2]{
    \begin{tabular*}{0.977\textwidth}{l@{\extracolsep{\fill}}r}
        \tiny{$\bullet$}\hspace{7pt}\small{#1} & \textit{\small{#2}} \\
    \end{tabular*}\vspace{-11pt}
}

\newcommand{\resumeItemAlt}[2]{
    \begin{tabular*}{0.977\textwidth}{l@{\extracolsep{\fill}}r}
        \tiny{$\bullet$}\hspace{7pt}\small{#1} & \textit{\footnotesize #2} \\
    \end{tabular*}
}
\newcommand{\resumeItemAltListStart}{\begin{adjustwidth}{10.8pt}{}}
\newcommand{\resumeItemAltListEnd}{\end{adjustwidth}}

\newcommand{\resumeStatementBasic}[2]{
    \begin{tabular*}{0.993\textwidth}{l@{\extracolsep{\fill}}r}
      \small{#1} & \textit{\footnotesize #2} \\
    \end{tabular*}
}

%%%%%%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%-----------Profile-----------
% \newcommand{\name}{Laxman Desai}
% \newcommand{\email}{desai.laxman2001@gmail.com}
% \newcommand{\contact}{(\Plus 91) 820-807-8914}
% \newcommand{\GithubUsername}{relaxxpls}
% \newcommand{\LinkedinUsername}{LaxmanDesai}

% \begin{center}
% 	\textbf{\Huge \name}\\
% 	\vspace{10pt}
% 	\small \faMobile* \contact \quad$|$\quad
% 	\href{mailto:\email}{\faEnvelope\ \underline{\email}} \quad$|$\quad
% 	\href{https://linkedin.com/in/\LinkedinUsername}{\faLinkedin\ \underline{\LinkedinUsername}} \quad$|$\quad
% 	\href{https://github.com/\GithubUsername}{\faGithub\ \underline{\GithubUsername}}
% \end{center}

%-----------EDUCATION-----------
% \section{Education}
% \resumeSubHeadingListStart
%   \resumeSubheading
%   {Indian Institute of Technology, Bombay}{Mumbai, India}
%   {Bachelor of Technology}{2019 -- Present}
%   \resumeItemAltListStart
%     \resumeItemAlt{Majoring in Chemical Engineering}{(CGPA 8.19/10)}
%     \resumeItemAlt{Minoring in Machine Learning \& Data Science}{(CGPA 10.0/10)}
%   \resumeItemAltListEnd
% \resumeSubHeadingListEnd
  
% PT cell spacing
%   \vspace*{30mm}  %  short header
  \vspace*{40mm}  %  long  header

  \resumeStatementBasic
  {Pursuing a \textbf{Minor} in \textbf{Artificial Intelligence and Data Science} at IIT Bombay (CPI 10/10)}{(2021 - Present)}


%-----------Experience-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
  {Frontend Developer Intern}{(Jul. 2021 - Present)}
  {Board Infinity}{Mumbai, India}
  \resumeItemListStart
    \resumeItem{Working in an \textbf{agile} team to provide each new customer a personalized onboarding experience}
    \resumeItem{Building a \textbf{Next.js} and \textbf{Typescript} web page that can dynamically load forms using a \textbf{JSON Schema}}
  \resumeItemListEnd

  \resumeSubheading
  {Software Developer Intern}{(May. 2021 - Jul. 2021)}
  {Pay1}{Mumbai, India}
  \resumeItemListStart
    \resumeItem{Designed a CAPTCHA Solver library and utilized it to fully automate various services used by the company}
    \resumeItem{Built a Python \textbf{Flask} webserver with \textbf{Redis} cache that automated the Aadhaar eKYC process, reducing the operating costs by about \textbf{50\%} and provided a seamless onboarding experience for the new customers}
    \resumeItem{Utilized \textbf{Selenium} WebDriver to interact with the various portals \& tested the RESTful API using \textbf{Postman}}
    \resumeItem{Hand built and labeled \textbf{5} datasets containing \textbf{1500\Plus} sample images and preprocessed them using \textbf{OpenCV}}
    \resumeItem{Extracted the features using a convolution-based algorithm in NumPy and trained a CNN \textbf{PyTorch} model to make predictions, achieving an average accuracy of \textbf{92\%} on the 5 different text CAPTCHA datasets analyzed}
    \resumeItem{Awarded a \textbf{Letter of Recommendation} by the company’s CTO for the exceptional impact of the project}
  \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
  {\href{https://github.com/relaxxpls/ResoBin}{\textbf{ResoBin}} $|$ \emph{ReactJS, Redux, Python, Django Rest Framework, SQLite}}{(Mar. 2021 - Present)}
  {Summer of Code, IIT Bombay}{}
  \resumeItemListStart
    \resumeItem{Developed a fully responsive website for students to share the course material, lecture notes, and quiz papers}
    \resumeItem{Designed an intuitive and elegant frontend interface using \textbf{Figma} and then built it on the \textbf{ReactJS} framework}
    \resumeItem{Utilised \textbf{Redux} for globally managing the application's state and \textbf{Axios} for making asynchronous API calls}
    \resumeItem{Created pagination alongside a debounced async search that provided a pleasant course browsing experience}
    \resumeItem{Built a \textbf{Django} backend server with \textbf{SQLite} database and utilised \textbf{JWT} authorisation for user sign up \& login}
  \resumeItemListEnd

  \resumeProjectHeading
  {\href{https://github.com/relaxxpls/StockPrediction}{\textbf{NIFTY 50 Stock Prediction}} $|$ \emph{Python, TensorFlow, statsmodels, pandas, sklearn}}{(Feb. 2021 - Apr. 2021)}
  {Course: Machine Learning, IIT Bombay}{Prof. Biplab Banerjee, C-MInDS}
  \resumeItemListStart
    \resumeItem{Analysed the prediction capabilities of time series forecasting models on the daily opening price of stocks}
    \resumeItem{Performed the analysis on the NIFTY 50 stock's 8 year long dataset acquired from Yahoo Finance}
    \resumeItem{Utilised a sliding window approach to predict the outcome of the $15^{th}$ day by training on the previous 14 days}
    \resumeItem{Built an \textbf{ARIMA} model using the \textbf{statsmodels} package, which achieved the lowest testing Mean Square Error}
    \resumeItem{Studied various \textbf{RNN} models such as stacked \& bidirectional \textbf{LSTMs} built using the \textbf{TensorFlow} framework}
  \resumeItemListEnd

  \resumeProjectHeading
  {\href{https://github.com/relaxxpls/Optimize-Heating-Indoors}{\textbf{Optimize Heating Indoors}} $|$ \emph{Python, SymPy, NumPy, Matplotlib}}{(Feb. 2021 -- Apr. 2021)}
  {Course: Heat Transfer, IIT Bombay}{Prof. P. Sunthar, ChE}
  \resumeItemListStart
    \resumeItem{Studied \& analysed methods to reduce energy consumption in large buildings situated in hot \& dry places}
    \resumeItem{Implemented a solution comprising of a thin water layer that causes evaporation resulting in a 5\% heat drop}
    \resumeItem{Solved resulting PDEs in Python with \textbf{NumPy} \& \textbf{SymPy} and visualised the result data using \textbf{Matplotlib}}
  \resumeItemListEnd

  \resumeProjectHeading
  {\href{https://github.com/relaxxpls/Optimize-Heating-Indoors}{\textbf{CPPMatrixLib}} $|$ \emph{C\Plus\Plus, CMake, GoogleTest}}{(Jan. 2021 -- Mar. 2021)}
  {Summer of Code, IIT Bombay}{}
  \resumeItemListStart
    \resumeItem{Designed and implemented a lightweight, dependency-free, templated numerical analysis library for C\Plus\Plus}
    \resumeItem{Led the implementation of algorithms such as LU \& QR Decomposition, Prime Tests, ModInt, and the FFT}
    \resumeItem{Mentored students to setup unit testing for the library using \textbf{CMake} and the GoogleTest framework}
  \resumeItemListEnd

\vspace{1cm}
  \resumeProjectHeadingAlt
  {\href{https://github.com/relaxxpls/TeXURL}{\textbf{TeXURL}} $|$ \emph{Python, Requests, \LaTeX, RegEx}}{(Mar. 2021 - Ongoing)}
  \resumeItemListStart
    \resumeItem{Created a Python package to allow \LaTeX\ to render images from links similar to HTML or Markdown}
    \resumeItem{Utilised \textbf{RegEx} to search \LaTeX\ code for valid URLs and \textbf{Requests} to download \& link the local version}
    \resumeItem{Optimized by identifying and avoiding duplicate downloads through file hashing with the \textbf{Adler-32} hash}
  \resumeItemListEnd

  \resumeProjectHeading
  {\href{https://github.com/relaxxpls/smarty}{\textbf{Self Navigating Suitcase}} $|$ \emph{Python, OpenCV, ROS, Gazebo}}{(Mar. 2020 - Jul. 2020)}
  {Institute Technical Summer Project, IIT Bombay}{}
  \resumeItemListStart
    \resumeItem{Designed a smart suitcase that can visually recognise and follow an \textbf{ArUco} marker carried by its owner}
    \resumeItem{Implemented computer vision using Python \& OpenCV to scan the surroundings and lockdown on the target through the HSV color range and used centroid tracking for mimicking the motion of the target}
  \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Achievements}
\resumeItemAltListStart
	\resumeItemAlt
    {\textbf{4\hspace{1pt}$\star$} at CodeChef \href{https://www.codechef.com/users/relaxxpls}{(relaxxpls)} and \textbf{1048\textsuperscript{th}} amongst \textbf{15k\Plus} participants in Googe Kickstart Sept. `20}
    {(2020)}
	\resumeItemAlt
    {Secured \textbf{AIR 1448} amongst \textbf{15lakh} other candidates in JEE Advanced}
    {(2019)}
	\resumeItemAlt
    {Secured \textbf{AIR 1063} amongst \textbf{10lakh} other candidates in AIIMS Entrance Test}
    {(2019)}
	\resumeItemAlt
    {Secured \textbf{99.6\%ile} in JEE Mains and \textbf{98.7\%ile} in NEET amongst \textbf{18lakh} candidates}
    {(2019)}
	\resumeItemAlt
    {Physics \textbf{topper} and overall \textbf{2nd} ranker in GCET among \textbf{20k\Plus} other candidates}
    {(2019)}
	\resumeItemAlt
    {Scored \textbf{396/450} in BITSAT placing in top \textbf{0.1\%ile} of applicants}
    {(2019)}
	\resumeItemAlt
    {Goa State Talent Search Examination scholar for \textbf{2} consecutive years}
    {(2018 -- 2019)}
\resumeItemAltListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\techSkillListStart
  \techSkill{Languages}{C\Plus\Plus 17, Python, JavaScript/TypeScript, HTML, CSS/SASS, \TeX, Java, Matlab, Powershell, Bash}
  \techSkill{Development}{ReactJS, Redux, Next.js, Django, Flask, Selenium, Redis, Git, Postman, VSCode, PostgreSQL}
  \techSkill{Machine Learning}{Torch, OpenCV, TensorFlow, Keras, Jupyter, Pandas, NumPy, SKLearn, SciPy, Matplotlib}
\techSkillListEnd


%-----------PoRS-----------
\section{Position of Responsibility}
\resumeSubHeadingListStart
  \resumeSubheading
  {UI Development Lead}{(Jun. 2021 -- Present)}
  {Developers Community, IIT Bombay}{Mumbai, India}
  \resumeItemListStart
    \resumeItem{Mentored the junior developers in the ideation and development of various institute-wide web projects}
    \resumeItem{Contributed to the development of Creddit, a course related opinions and Q\&As website}
  \resumeItemListEnd

  \resumeSubheading
  {Design Secretary}{(Apr. 2020 -- Apr. 2021)}
  {Chemical Engineering Association, IIT Bombay}{Mumbai, India}
  \resumeItemListStart
    \resumeItem{Crafted posters and curated content for promoting \textbf{10\Plus} departmental events, totaling a {200\Plus} attendance}
    \resumeItem{Designed Chemical Gazette, the annual magazine alongside the Freshmen Newsletter \& the department hoodie}
    \resumeItem{Utilized \textbf{Adobe Creative Cloud} (Illustrator, InDesign, Photoshop, Premiere Pro, and After Effects)}
  \resumeItemListEnd

  \resumeSubheading
  {Institute Cultural Mentor}{(Jun. 2020 -- May. 2021)}
  {Culturals, IIT Bombay}{Mumbai, India}
  \resumeItemListStart
    \resumeItem{Led a team of \textbf{20\Plus} students to manage the media and publicity of Showstopper, gathering an audience of \textbf{500\Plus}}
    \resumeItem{Conceptualized Style Saturday, a blog aimed at promoting personal well being resulting in 2$\times$ engagement}
  \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------Courses-----------
\section{Key Courses}
\techSkillListStart
  \techSkill{Computer Science}{Machine Learning, Deep Learning\textsuperscript{\textdagger}, DSA (Summer of Science `20), Digital Image Processing\textsuperscript{\textdagger}}

  \techSkill{Chemical Engg}{Chemical Reaction Engineering\textsuperscript{\textdagger}, Mass Transfer\textsuperscript{\textdagger}, Heat Transfer, Computational Methods, \\\hspace{29mm} Fluid Mechanics, Solid Mechanics\textsuperscript{\textdagger}, Thermodynamics \hspace{1cm} [\textdagger\ : to be completed by Nov. `21]}

  \techSkill{Mathematics}{Data Analysis, Numerical Analysis, Calculus, Linear Algebra, Differential Equations}
\techSkillListEnd

%-----------EXTRACURRICULAR-----------
\section{Extracurricular}
\resumeItemAltListStart
	\resumeItemAlt
    {Successfully completed a 2 week long internship program at the Proteomics Lab, IIT Bombay}
    {(Jun. 2021)}
    \resumeItemAlt
    {Produced an EDM song and released it on Spotify as a part of Institute Cultural Summer Project}
    {(Aug. 2020)}
	\resumeItemAlt
    {Successfully completed a finance bootcamp organized by the Finance Club, IIT Bombay which}
    {(Apr. 2020)}
	\vspace{-2pt} \hspace{3.75mm}{\small taught and tested the knowledge of Financial Statements, Capital Markets \& Ratio Analysis}\vspace{2pt}
	\resumeItemAlt
    {Participated in StyleUp's Showstopper 2020 and performed to an audience of \textbf{1000\Plus}}
    {(Jan. 2020)}
	\resumeItemAlt
    {Professionally trained in table tennis through the National Sports Organization (NSO)}
    {(2019 - 2020)}
	\resumeItemAlt
    {Directed, edited, and starred in a \textbf{3\textsuperscript{rd}} prize-winning comedy video \textit{Area 51 Leaks}, made as an}
    {(Sep. 2019)}
	  \vspace{-2pt} \hspace{3.75mm}{entry for Freshiezza `19, the freshmen festival}\vspace{2pt}
	\resumeItemAlt
    {Built a remote controlled car and competed in navigating an obstacle race course - XLR8 `19}
    {(Sep. 2019)}
	\resumeItemAlt
    {Played football (midfielder) for Sharada Mandir School team at state level}
    {(2015 - 2016)}
\resumeItemAltListEnd

\end{document}
