\documentclass[a4paper,11pt]{article}
\usepackage[strict]{changepage}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage[a4paper]{geometry}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\geometry{left=1.9cm, top=1.8cm, right=1.9cm, bottom=1.8cm, footskip=.5cm}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%------------------ Custom commands ------------------- 
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.977\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[4]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
      \textit{\small#3} & \textit{\small #4}\\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=-0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\cvrank}[2]{\small{\textit{#1} \textbf{#2} $\bullet$}}
\newcommand{\cvrankend}[2]{\small{\textit{#1} \textbf{#2} \\ }
}


\newcommand{\extracurr}[2]{
    \begin{tabular*}{0.977\textwidth}{l@{\extracolsep{\fill}}r}
        \tiny{$\bullet$}\hspace{7pt}\small{#1} & \textit{\small{#2}} \\
    \end{tabular*}\vspace{-11pt}
}


%%%%%%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%
\begin{document}
  \vspace*{4cm}
  %-----------Internships-----------
  \section{Internships}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Tech Leaders Summer Fellow}{(Jun. 2020 - Aug. 2020)}
        {Camp K12}{Mumbai, India}
        \resumeItemListStart
          \resumeItem{Taught coding in an intuitive manner to \textbf{100}\footnotesize{+} \small students aged 14\hspace{2pt}-\hspace{1pt}18 years using \textbf{Python} and \textbf{JavaScript}}
          \resumeItem{Spearheaded the redesign \& diversification of the existing curriculum leading to \textbf{15\%} increase in revenue}
          \resumeItem{Covered curriculum spanning from basics such as Iterators to complex algorithms like Divide \& Conquer}
          \resumeItem{Utilized AI Playground, Repl.it, Hatch XR, and MIT App Inventor}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
  
  %-----------PROJECTS-----------
  \section{Projects}
      \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Smart Suitcase} $|$ \emph{Python, OpenCV, ROS, Gazebo, RViz, RQT}}{(Mar. 2020 - Jul. 2020)}{Institute Technical Summer Project, IIT Bombay}{Guide: Vishwajeet Bhagyawant}
            \resumeItemListStart
              \resumeItem{Designed a suitcase that follows its owner there by eliminating the trouble of carrying it around} 
              \resumeItem{Tested its functioning through virtual simulation by deploying it on a user controlled test target}
              \resumeItem{Implemented image processing through \textbf{Python} \& \textbf{OpenCV} to scan the surroundings and lock down on the target through the \textbf{HSV} color range and used centroid tracking for mimicking the targets motion}
              \resumeItem{Accurately \& efficiently simulated the bot and the control target using \textbf{Gazebo}, while using \textbf{ROS} to facilitate low-level device control and communication between various sub-processes}
            \resumeItemListEnd
    %---------
        \resumeProjectHeading
            {\textbf{Remote Controlled Airplane} $|$ \emph{IoT}}{(Sep. 2019 - Oct. 2019)} {Aeromodelling Club, IIT Bombay}{}
            \resumeItemListStart
              \resumeItem{Designed fuselage, stabilizers and wings to reduce drag and enhance the performance} 
              \resumeItem{Investigated design parameters for optimum performance and stability during flight}
            \resumeItemListEnd
    %---------    
        \resumeProjectHeading
            {\textbf{Wireless Remote Controlled Car} $|$ \emph{IoT}}{(Aug. 2019 - Sep. 2019)} {Electronics \& Robotics Club, IIT Bombay}{}
            \resumeItemListStart
              \resumeItem{Built a bot which decodes Bluetooth signals using an \textbf{ATtiny} IC to overcome an obstacle-filled course} 
              \resumeItem{Installed \textbf{HC05} Bluetooth module to operate the bot remotely using an Android app}
              \resumeItem{Implemented differential steering mechanism via \textbf{L293D} motor driver for reducing the turning radius}
            \resumeItemListEnd

      \resumeSubHeadingListEnd

  %-----------PROGRAMMING SKILLS-----------
  \section{Achievements}
    \begin{adjustwidth}{10.8pt}{}
          \extracurr{\textbf{4\hspace{1pt}$\star$} at CodeChef (relaxxpls) and \textbf{1048\textsuperscript{th}} amongst \textbf{9000+} participants in Googe Kickstart} {(Sept. 2020)}
          
          \extracurr{Secured \textbf{AIR 1448} amongst \textbf{15lakh} other candidates in JEE Advanced}{(2019)}
          
          \extracurr{Secured \textbf{AIR 1063} amongst \textbf{10lakh} other candidates in AIIMS Entrance Test}{(2019)}
          
          \extracurr{Secured \textbf{99.6\%ile} in JEE Mains and \textbf{98.7\%ile} in NEET amongst \textbf{18lakh} candidates}{(2019)}
          
          \extracurr{\textbf{Physics Topper} and overall \textbf{2nd} Ranker in GCET among \textbf{10,000} other applicants} {(2019)}
          
          \extracurr{Scored \textbf{396/450} in BITSAT placing in top \textbf{0.1\%ile} of applicants}{(2019)}
          
          \extracurr{Goa State Talent Search Examination scholar for \textbf{2} consecutive years}{(2018 - 2019)}
        
    \end{adjustwidth}

  %-----------PROGRAMMING SKILLS-----------
  \section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
          \textbf{Languages}{: C/C++, Python, Java, JavaScript, HTML/CSS, Bash, Matlab, R} \\ 
        \vspace{1.3mm}
          \textbf{Tools}{: Git, PowerShell, Sublime Text, \LaTeX, AutoCAD, SolidWorks, ROS, CMake, Adobe Creative Cloud} \\ 
        \vspace{1.3mm}
          \textbf{Libraries}{: STL, NumPy, OpenCV, TKinter} 
        }}
    \end{itemize}

  %-----------PoRS-----------
  \section{Position of Responsibility}
    \resumeSubHeadingListStart
      
      \resumeSubheading
        {Design Secretary}{(Apr. 2020 - Ongoing)}
        {Chemical Engineering Association (ChEA), IIT Bombay}{Mumbai, India}
        \resumeItemListStart
          \resumeItem{Part of a \textbf{9} member team, selected out of \textbf{50+} students on the basis of manifesto, assignment \& interview}
          \resumeItem{Co-organised and coordinated \textbf{20+} departmental events, managing \textbf{1000+} unique students in total}
          \resumeItem{Crafted posters, curated content, designed new and innovative department hoodies leading to higher sales}
          \resumeItem{Utilised \textbf{CorelDraw} \& \textbf{Adobe Creative Cloud} (Illustrator, Photoshop, Premiere Pro \& After Effects)}
      \resumeItemListEnd
  %---------
      \resumeSubheading
        {Institute Cultural Mentor}{(Jun. 2020 - Ongoing)}
        {StyleUp - The Fashion Club, Culturals, IIT Bombay}{Mumbai, India}
        \resumeItemListStart
          \resumeItem{Nominated (\textbf{4} out of \textbf{100}+) by Institute Fashion Nominee to promote fashion \& other cultural activities}
          \resumeItem{Conceptualized and spearheaded Style Saturday, a monthly blog aimed at promoting style, grooming and personal well being amidst the COVID lock down resulting in \textbf{2$\times$} monthly engagement}
          \resumeItem{Led the ideation \& execution of various genre related events, targeting \textbf{300\%} \textbf{increase} in participation by introducing mixed themes, using innovative publicity, and introducing large scale never before seen online events such as Glamour Grande, an online fashion show}
        \resumeItemListEnd
  %---------    
      \resumeSubheading
        {Robowars Organizer}{(Oct. 2019 - Jan. 2020)}
        {Techfest, IIT Bombay}{Mumbai, India}
        \resumeItemListStart
        \resumeItem{Part of a team organising Asia’s largest college technological festival, handling a total footfall of \textbf{1lakh}+}
        \resumeItem{Led a group of \textbf{10+} organizers handling the sound system at India's largest robot combat competition}
      \resumeItemListEnd
      
    \resumeSubHeadingListEnd    


  %-----------Courses-----------
  \section{Key Courses}
    \begin{adjustwidth}{10.8pt}{}
    \resumeSubHeadingListStart
      \resumeSubSubheading 
        {\textbf{\textsc{Computer Sci. : }}Cryptography \& Network Security\textsuperscript{\textdagger}, Introduction to Machine Learning\textsuperscript{\textdagger}, Data Analysis\textsuperscript{\textdagger}}{}
        \vspace{-0.35cm}
      \resumeSubSubheading
        {\hspace{3.05cm}DSA Specialization (UC San Diego, Coursera), Machine Learning\textsuperscript{\textdagger} (CS50 Harvard, edX)}{}
        \vspace{-0.35cm}
      \resumeSubSubheading
        {\hspace{3.05cm}Data Structures \& Algoritms (Summer Of Science '20)}{[\ \textdagger\ : To be completed by Apr '21]}
        \vspace{-0.35cm}
  %---------    
      \resumeSubSubheading
        {\textbf{\textsc{Mathematics \hspace{3.5mm}: }}Numerical Analysis, Linear Algebra, Differential Equations, Discrete Structures\textsuperscript{\textdagger}}{}
        \vspace{-0.35cm}
  %---------
      \resumeSubSubheading
        {\textbf{\textsc{Chemical Eng. : }}Process Fluid Mechanics\textsuperscript{\textdagger}, Heat Transfer\textsuperscript{\textdagger}, Thermodynamics, Computational Methods}{}
        \vspace{-0.3cm}
    \resumeSubHeadingListEnd    
    
    \end{adjustwidth}

  %-----------EXTRACURRICULAR-----------
  \section{Extracurricular}
    \begin{adjustwidth}{10.8pt}{}
      \extracurr{Mentored \textbf{200+} UG \& PG freshers and introduced them to various cultural activities}{(Sept. 2020)}
      
      \extracurr{Successfully completed a Finance Bootcamp organised by Finance Club, IIT Bombay which}{(Apr. 2020)}
      
      \vspace{-2pt} \hspace{3.75mm}{\small taught and tested the knowledge of Financial Statements, Capital Markets \& Ratio Analysis}
      
      \vspace{2pt}
      \extracurr{Produced a song and released it on Spotify as a part of Institute Cultural Summer Project}{(Aug. 2020)}
      
      \extracurr{Participated in StyleUp's Showstopper 2020 and performed to an audience of \textbf{1000+}}{(Jan. 2020)}
      
      \extracurr{Professionally trained in table tennis through the National Sports Organization (NSO)} {(2019 - 2020)}
      
      \extracurr{Directed, Edited and Starred in a \textbf{3\textsuperscript{rd}} Prize winning comedy video "Area 51 Leaks",}{(Sep. 2019)}
      
      \vspace{-2pt} \hspace{3.75mm}{made as an entry for the freshmen festival (Freshiezza)}
      
      \vspace{2pt}
      \extracurr{Played football (midfielder) for Sharada Mandir School team at state level}{(2015 - 2016)}
    
    \end{adjustwidth}
    
\end{document}